Large scale agile transformations: A literature review

### 2013-01-25 tex/article.tex
Text for challenges

Typical challenges and and success factors reported in the studies are listed in
Table \ref{table:success}.

@@

        \raggedright\rule{0pt}{0.4cm}Misunderstanding the agile model  &
             Wrong application of roles and responsibilities \newline
             [S6, S10, S11, S13, S17, S23, S24] \\

        \raggedright\rule{0pt}{0.4cm}Effect of agile outside of development  &
            Conflicts with business (eg. planning) [S6, S11, S21] \newline
            Making non-development functions agile (testing, maintenance, etc.) [S2, S4, S13]\newline
            Conflicts with other functions (marketing, HR, etc.) \newline[S6, S10, S11, S13] \\

>>>>

Typical challenges and and success factors reported in the studies are listed in
Table \ref{table:success}. In both cases the ability to align the organization
was a central factor in both cases. Challenges surface if not everyone is on
board with the change. Good ground for the change is created by strongly
communicating a clear vision and enabling everyone to participate. Resourcing
for the change was also seen both as a challenge and a success factor.
The studies show that allocating extra training and hiring of external consultants
facilitate the change.

A particular challenge for adopting agile was misunderstanding how agile should
be applied. Some symptoms of this were talking agile but still working the old
way, and managers making commitments without hearing development teams.
As expected, many studies reported that development teams had problems
interfacing with other organizational functions, such as management and
marketing.

@@

        \raggedright\rule{0pt}{0.4cm}Misunderstanding the agile model  &
             Wrong application of roles and responsibilities \newline
             [S11, S13, S16, S17, S23, S24] \newline
             Agile terms merely mask the old model [S10, S22] \\

        \raggedright\rule{0pt}{0.4cm}Effect of agile outside of development  &
            Conflicts with business (e.g. planning) [S6, S11, S21] \newline
            Making non-development functions agile (testing, maintenance, etc.) [S2, S4, S13]\newline
            Conflicts with other functions (marketing, HR, etc.) \newline[S6, S10, S11, S13] \\
